### 2018-05-22 2_wmm.tex
Move x86 example from appendix to the text.

For instance, the \fr-relation is defined as a sequence of inverted \rf-relation and \co-relation: $\texttt{fr} = (\invrel{rf};\texttt{co})$.
As an example of memory model definition in \cat{} language, the x86-TSO model~\cite{herd10tutorial} can be found in Appendix~\ref{apx:x86cat}.
This memory model asserts acyclicity of communication relation, \texttt{po-loc} -relation, \texttt{mfence}-relation and some other derived relations~\cite{owens2009better}.

>>>>

For instance, the \fr-relation is defined as a sequence of inverted \rf-relation and \co-relation: $\texttt{fr} = (\invrel{rf};\texttt{co})$.
As an example of memory model definition in \cat{} language, Figure~\ref{ex:x86-cat} presents the simplified x86-TSO model~\cite{herd10tutorial}.
This memory model asserts  acyclicity of the communication relation (the union of \rf-, \fr- and \co- relations), \texttt{po-loc} -relation, \texttt{mfence}-relation and some other derived relations~\cite{owens2009better}.

\begin{figure}[h]
\begin{lstlisting}
"X86 TSO"
include "x86fences.cat"
include "filters.cat"
include "cos.cat"

(* Uniproc check *)
let com = rf | fr | co
acyclic po-loc | com

(* Atomic *)
empty rmw & (fre;coe)

(* Global happens-before *)
#ppo
let po_ghb = WW(po) | RM(po)

#mfence
include "x86fences.cat"

#implied barriers
let poWR = WR(po)
let i1 = MA(poWR)
let i2 = AM(poWR)
let implied = i1 | i2

let com = rfe | fr | co
let ghb = mfence | implied | po_ghb | com
show implied

acyclic ghb as tso
\end{lstlisting}
\caption{The simplified x86-TSO memory model defined in the \cat{} language~\cite{herd10tutorial}}
\label{ex:x86-cat}
\end{figure}
